\begin{abstract}
A multi-site experiment supports its external-validity claim through a cross-site moment identity $\Sigma\theta + b = 0$. When the number of sites $S$ is small relative to the site-level covariate dimension, this identity is rank-deficient and leaves the target-site treatment effect only partially identified. In recent work, \citet*{boyarsky2026} formalize this partial identification and derive debiased bounds on $\psi(\theta;\gamma)$ at a user-chosen target profile $(t_m,t_r)$ under analyst-specified affine restrictions $r(\theta)\le 0$. In this work we study the \emph{inverse} design question. Given a pool of candidate sites with known site-level context $(C_m^{(k)},C_r^{(k)})$ but no experimental data, which site should an investigator go and run to most strengthen external-validity claims about a population of target profiles? We formulate the problem as a minimax design over the width of the partial-identification region. We establish a geometric characterization that, without restrictions, reduces to an ``expand-the-convex-hull'' rule for the site-level context vectors. Under compact affine restrictions, we derive a tractable surrogate. The criterion has the same three-regime structure as the leave-one-site-out diagnostic of \citet{boyarsky2026}: candidate sites either (i) strictly reduce the null space of $\Sigma$ and can collapse unbounded widths to finite ones, (ii) translate the moment-implied affine subspace closer to the target profile at fixed rank, or (iii) restore feasibility of substantive restrictions that were incompatible with the existing pool.  We also give sufficient conditions under which adding a site does not increase the worst-case width. We illustrate these findings on synthetic data. In our simulations, candidate sites that satisfy our conditions reduce the minimax width. Together, these results give practitioners a simple rule for choosing the next site to strengthen the external validity of experimental findings.
\end{abstract}
