\section{The Minimax Criterion under Affine Restrictions}
\label{sec:restrictions}

Compact affine restrictions $\mathcal{R} = \{\theta : r(\theta)\le 0\}$ (e.g.,
box constraints, effect-ordering, sign/monotonicity) replace the unbounded
behavior in the null space of Proposition~\ref{prop:dichotomy} with a finite LP
whose width we can compute and optimize.

\subsection{A tractable surrogate}
\label{sec:surrogate}

Fix a candidate $k$ and a target $(t_m, t_r)$. The width is the value of the LP
pair \eqref{eq:bounds} with $\Sigma \leftarrow \Sigma_{\mathcal{S}\cup\{k\}}$.
Because $\Delta\Sigma_k$ has rank at most $2$, the candidate's effect on the
feasible set is a \emph{rank-2 perturbation} of the affine subspace
$\{\Sigma_\mathcal{S}\theta = -b\}$. Under Assumption~6 of \citet{boyarsky2026} (Robinson constraint qualification) the LP values are Lipschitz in
$\Sigma$, and we obtain a first-order surrogate:

\begin{proposition}[Rank-2 envelope, endpoint-specific]
\label{prop:envelope}
Fix a target $t$ and assume the upper and lower LPs in \eqref{eq:bounds} each
have a unique optimal primal--dual pair (strict complementarity). Let
$(\theta_u^\star,\lambda_u^\star)$ and $(\theta_\ell^\star,\lambda_\ell^\star)$
be the optimal primal solution and equality multiplier of the upper ($\max$) and
lower ($\min$) problems at $\Sigma_\mathcal{S}$, each with the sign convention of
its own Lagrangian. Then the directional derivatives of the endpoints along the
site-update direction $(\Delta\Sigma_k,\Delta b_k)$ are
\begin{equation}
\label{eq:envelope}
D v_u \;=\; -\,\lambda_u^{\star\top}\bigl(\Delta\Sigma_k\,\theta_u^\star+\Delta b_k\bigr),
\qquad
D v_\ell \;=\; -\,\lambda_\ell^{\star\top}\bigl(\Delta\Sigma_k\,\theta_\ell^\star+\Delta b_k\bigr),
\end{equation}
and the first-order change in the width is $D w_k = D v_u-D v_\ell$. This
collapses to a single $-(\lambda_u^\star-\lambda_\ell^\star)^\top
(\Delta\Sigma_k\,\theta^\star+\Delta b_k)$ only in the degenerate zero-width case
$\theta_u^\star=\theta_\ell^\star$; in general the optimizers, active sets, and
multipliers differ and must be kept separate. Without strict complementarity,
$D v_u$ and $D v_\ell$ are the $\max$ and $\min$ of \eqref{eq:envelope} over the
optimal primal--dual solution sets.
\end{proposition}

Proposition~\ref{prop:envelope} is the Bonnans--Shapiro directional derivative of
the constrained-value map, specialized to the finite-dimensional rank-2
site-update direction $(h_\Sigma, h_b) = (\Delta\Sigma_k/\|\Delta\Sigma_k\|,
\Delta b_k)$. The formula \eqref{eq:envelope} coincides with Equation~(1.3) of \citet{boyarsky2026}, evaluated at the site-augmentation direction. It gives a \emph{linear-in-$k$} surrogate for the width change. Because a
candidate that shrinks the width has $D w_k<0$, the selection minimizes the
\emph{signed} first-order width, not its magnitude:
\begin{equation}
\label{eq:surrogate}
k^\star_{\rm surr}\;\in\;\arg\min_{k\in\mathcal{K}}\;
 \sup_{(t_m,t_r)\in\mathcal{T}}\;
 \Bigl[\,w_\mathcal{S}(t)\;+\;\overline{Dw}_k(t)\,\Bigr],
\qquad
\overline{Dw}_k(t):=
 -\lambda_u^{\star\top}\Delta\Sigma_k\theta_u^\star
 +\lambda_\ell^{\star\top}\Delta\Sigma_k\theta_\ell^\star
 +\sup_{\Delta b_k\in\mathcal{B}}\bigl(\lambda_\ell^\star-\lambda_u^\star\bigr)^\top\Delta b_k,
\end{equation}
where the last term robustifies over the unknown $\Delta b_k$ in the prior ball
$\mathcal{B}$ via a dual-norm bound and is additive in the candidate. Replacing
the bracket by $\bigl|D w_k(t)\bigr|$, as in an earlier draft, is incorrect: it
penalizes precisely the width-shrinking candidates (those with $D w_k<0$).
Computing \eqref{eq:surrogate} requires solving the LP pair \eqref{eq:bounds} at
$\Sigma_\mathcal{S}$ once per target and a finite-dimensional matrix--vector
product per candidate, total cost $O(|\mathcal{T}|\cdot K)$.

\subsection{Three regimes}
\label{sec:regimes}

The linearization \eqref{eq:envelope} inherits the three-regime taxonomy of the
LOO diagnostic of \citet[\S4.4]{boyarsky2026}, now read in reverse:

\begin{itemize}
\item \textbf{(A) Coverage-expanding candidate.} If $(C_m^{(k)}, C_r^{(k)})
  \notin \mathrm{aff}(\mathcal{H}_\mathcal{S})$, then
  $\mathrm{null}(\Sigma_{\mathcal{S}\cup\{k\}}) \subsetneq
  \mathrm{null}(\Sigma_\mathcal{S})$. Proposition~\ref{prop:envelope} detects
  this as a first-order contraction of the width whenever the binding recession
  direction at target $t$ lies along the newly-resolved null-space direction. In
  the unrestricted limit this regime collapses infinite widths to finite
  ones.

\item \textbf{(B) Location-improving candidate.} If $(C_m^{(k)}, C_r^{(k)}) \in
  \mathrm{aff}(\mathcal{H}_\mathcal{S})$ but outside the convex hull, the rank of
  $\Sigma$ does not change but $\Delta b_k$ translates the moment-implied affine
  subspace. The binding vertex of the LP can shift, which gives a first-order
  width change of either sign. This is the regime in which a new site
  improves
  overlap at the target without adding a new identification direction.

\item \textbf{(C) Feasibility-restoring (or -breaking) candidate.} If $\{\theta
  : \Sigma_\mathcal{S}\theta = -b_\mathcal{S}\}\cap \mathcal{R} = \emptyset$, an
  infeasibility signaled by the Farkas alternative of \citet[\S4.4 (c)]{boyarsky2026}, a candidate $k$ can restore feasibility if its site-update
  direction pushes the affine subspace back into $\mathcal{R}$.
  Conversely, a candidate whose direction is incompatible with the existing
  restriction set can break feasibility, which is diagnostic information rather
  than a reason to exclude the candidate.
\end{itemize}

The minimax selection \eqref{eq:minimax} therefore does not reduce to a single
geometric quantity in general. The convex-hull rule is exact in regime (A) and
the unrestricted limit, and it is a useful first screen that should be refined
by \eqref{eq:surrogate} when the restriction set is binding.

\subsection{Handling the unknown \texorpdfstring{$\Delta b_k$}{Delta b\_k}}
\label{sec:unknown-b}

The right-hand-side update $\Delta b_k$ depends on the candidate site's future
outcomes. Three prior choices are natural:

\begin{enumerate}
\item \textbf{Uninformative ball.} $\Delta b_k \in \{b : \|b\|_2 \le B\}$. Yields
  a worst-case width via dual-norm bound, but can dominate $\Delta\Sigma_k$ at
  small candidate sample sizes. Conservative.

\item \textbf{Meta-analytic prior.} Use the existing-pool estimates as a prior on
  the candidate's $(Y, A)$ conditional means, and propagate through the
  expression for $b$ in Equation~(A.7) of \citet{boyarsky2026}. We expect that
  under a flat prior on $\theta$ this behaves like a Bayesian D-optimal design,
  with the minimax and Bayesian selections coinciding in the
  large-candidate-sample limit; we state this as a heuristic guide rather than a
  theorem and do not prove it here.

\item \textbf{Adversarial $b$.} $\Delta b_k \in \mathcal{B}$ chosen to maximize
  the width, the robust-optimization analogue of (1) with an ellipsoidal
  $\mathcal{B}$. The inner problem $\max_{\Delta b_k\in\mathcal{B}} w$ is the
  maximization of a concave function (the width is a concave upper value minus a
  convex lower value of $b$) over a convex set, hence tractable for each fixed
  $k$. A full Sion-minimax exchange with the candidate choice is not available in
  general because the candidate index is discrete; we solve the outer
  minimization by enumeration over $\mathcal{K}$.
\end{enumerate}

In our simulation (Section~\ref{sec:simulation}) we adopt (1) with $B$ set from
the existing-pool residual variance. The three variants agree on the
minimax-optimal candidate in all our runs. This is expected, because the rank
update in \eqref{eq:dsigma} dominates the first-order width change in the
regimes where candidates differ meaningfully.
