\section{Affine-Span (Convex-Hull) Expansion}
\label{sec:hull}

The minimax objective \eqref{eq:minimax} has a simple geometric structure in the
unrestricted limit $\mathcal{R} = \mathbb{R}^{d_g}$ (or equivalently, when the
restriction set is large enough that no face of $r$ binds at the optimum). In
this limit the partial-identification width is determined entirely by the
interaction between the null space of $\Sigma$ and the direction of the target
functional.

\subsection{Unrestricted dichotomy}
\label{sec:hull-dichotomy}

Write the linear target functional as $c(t)^\top \theta$ with
$c(t) := (\tilde c_m(t), \tilde c_r(t), 0, 0)$ (the zeros in the
$(\gamma_1, \gamma_2)$-coordinates follow because the target functional in
\eqref{eq:rep} is linear in $(\beta_1, \beta_2)$ only; the constant piece
$c_0(\gamma)$ shifts the endpoints but leaves the width invariant).

\begin{proposition}[Unrestricted width is $0$ or $\infty$]
\label{prop:dichotomy}
Let $\mathcal{R} = \mathbb{R}^{d_g}$. Then for any target direction $c(t)$ and
any feasible $b$,
\[
w_{\rm unr}(t; \Sigma, b) \;=\;
 \begin{cases}
  0 & \text{if } c(t)\in \mathrm{range}(\Sigma^\top), \\
  +\infty & \text{otherwise.}
 \end{cases}
\]
\end{proposition}

\begin{corollary}
\label{cor:collapse}
Adding a candidate site $k$ collapses the unrestricted width at target $t$ from
$\infty$ to $0$ if and only if the residualized context $(u_m^{(k)}, u_r^{(k)})$
of the candidate is such that
$c(t) \in \mathrm{range}\!\bigl(\Sigma_\mathcal{S}^\top + \Delta\Sigma_k^\top\bigr)$
but $c(t) \notin \mathrm{range}(\Sigma_\mathcal{S}^\top)$.
\end{corollary}

This is the unrestricted version of the \emph{coverage-expanding-donor} regime
(a) of the leave-one-site-out taxonomy in \citet[\S4.4]{boyarsky2026}.

\paragraph{Remark (Feasibility and fixed $\gamma$).}
Corollary~\ref{cor:collapse} presumes the augmented system remains feasible,
$b_{\mathcal{S}\cup\{k\}}\in\mathrm{range}(\Sigma_{\mathcal{S}\cup\{k\}})$; the
PSD update \eqref{eq:dsigma} guarantees this whenever the realized candidate
outcome is consistent with some $\theta$ (e.g.\ under (M2)). Throughout, the
functional $c(t)$ and the right-hand side $b$ are evaluated at a fixed $\gamma$
in the LP \eqref{eq:bounds}; only $\theta$ is optimized.

\subsection{The convex-hull interpretation}
\label{sec:hull-interp}

Proposition~\ref{prop:dichotomy} has a simple geometric interpretation in the
site-level context space. Let
\[
\mathcal{H}_\mathcal{S} \;:=\; \mathrm{conv}\!\bigl\{(C_m^{(s)}, C_r^{(s)})\,:\,
 s = 1, \ldots, S\bigr\} \;\subseteq\; \mathbb{R}^{d_M+d_I}.
\]
Its affine hull $\mathrm{aff}(\mathcal{H}_\mathcal{S})$ is a linear
subspace (after centering) of dimension at most $S-1$. The cross-site moment
matrix $\Sigma_\mathcal{S}$ has rank at most $\dim\mathrm{aff}(\mathcal{H}_\mathcal{S})
 \cdot (\text{block factor})$, with equality when the existing sites have
sufficient overlap in $X$ at the points where their contexts differ.

\begin{proposition}[Rank expansion $\Leftrightarrow$ affine-hull expansion]
\label{prop:hull}
Let $\bar c := \tfrac1S\sum_{s=1}^S (C_m^{(s)},C_r^{(s)})$, and write the
\emph{centered} contexts $\tilde c^{(s)} := (C_m^{(s)},C_r^{(s)})-\bar c$ and
$\tilde u := (C_m^{(k)},C_r^{(k)})-\bar c$. Let $\tilde C$ be the matrix with
rows $\tilde c^{(s)}$ and let the centered cross-site moment be
$\tilde\Sigma_\mathcal{S}=\tilde C^\top\tilde C$ in the simplified formulation.
If the candidate site's $X$-distribution has
positive density on the individual-level support, then
\[
\mathrm{rank}\bigl(\Sigma_{\mathcal{S}\cup\{k\}}\bigr)
 \;>\; \mathrm{rank}\bigl(\Sigma_\mathcal{S}\bigr)
\;\Longleftrightarrow\;
 \tilde u\notin\mathrm{range}\bigl(\tilde\Sigma_\mathcal{S}\bigr)
\;\Longleftrightarrow\;
 (C_m^{(k)},C_r^{(k)})\notin\mathrm{aff}(\mathcal{H}_\mathcal{S}),
\]
and in that case
$\mathrm{null}(\Sigma_{\mathcal{S}\cup\{k\}})\subsetneq\mathrm{null}(\Sigma_\mathcal{S})$.
\end{proposition}

\paragraph{Remark (Block/BEN version).}
For the residualized block moment of \eqref{eq:dsigma}, what is always true is
the range test:
$\mathrm{rank}(\Sigma_\mathcal{S}+\Delta\Sigma_k)>\mathrm{rank}(\Sigma_\mathcal{S})
 \iff \mathrm{range}(\Delta\Sigma_k)\not\subseteq\mathrm{range}(\Sigma_\mathcal{S})$.
The \emph{affine-hull} reading of Proposition~\ref{prop:hull} additionally
requires that the residualization embed contexts injectively: positive density
of the candidate's $X$-distribution alone does not guarantee that the raw
context direction maps injectively into the residualized moment range. We
therefore invoke the affine-hull equivalence for the block model only under the
explicit embedding assumption
$\mathrm{range}(\Sigma_\mathcal{S})=L_X\,\mathrm{span}\{\tilde c^{(s)}:s=1,\dots,S\}$
for an injective linear residualized-context map $L_X$; then a candidate context
outside $\mathrm{aff}(\mathcal{H}_\mathcal{S})$ is equivalent to rank expansion.

Combined with Proposition~\ref{prop:dichotomy}, this yields a
finite-versus-infinite dichotomy. Under no restriction $r$, the only candidate
sites that shrink the unrestricted width are those whose context lies outside
the \emph{affine hull} of the existing sites; we therefore call the exact rule
\emph{affine-span expansion}. Convex-hull coverage is a useful but strictly
weaker intuition: a target outside the convex hull but inside the affine hull
already has zero unrestricted width (it lies in $\mathrm{range}(\Sigma^\top)$),
so expanding the convex hull is the relevant picture only when the target region
$\mathcal{T}$ contains points outside $\mathrm{aff}(\mathcal{H}_\mathcal{S})$.

\subsection{Width-as-distance-to-hull}
\label{sec:hull-distance}

Proposition~\ref{prop:dichotomy}'s dichotomy is discontinuous, which is
uninformative for comparing two candidates both of which lie outside the hull, or
both of which lie inside. The correct continuous refinement uses a
\emph{regularized} width,
\begin{equation}
\label{eq:regwidth}
w_r^\tau(t; \Sigma, b) \;:=\; \max_\theta\{c(t)^\top\theta\} -
 \min_\theta\{c(t)^\top\theta\}\quad
\text{s.t.}\quad
\Sigma\theta+b = 0,\; \|\theta\|_2 \le \tau,
\end{equation}
with a large-radius ball as a mild stand-in for a compact restriction set. The
regularized width admits a closed form:
\begin{equation}
\label{eq:distbound}
w_r^\tau(t; \Sigma, b) \;\le\; 2\tau \cdot \mathrm{dist}\!\bigl(
 c(t),\; \mathrm{range}(\Sigma^\top)\bigr),
\end{equation}
with equality up to a boundary adjustment that vanishes at large $\tau$. The
distance from $c(t)$ to $\mathrm{range}(\Sigma^\top)$ is precisely the norm of the
component of $c(t)$ in $\mathrm{null}(\Sigma)$. Geometrically, this distance is a
monotone function of the distance from the target profile $(t_m, t_r)$ to
$\mathrm{aff}(\mathcal{H}_\mathcal{S})$, and strictly monotone under the rank
conditions of Proposition~\ref{prop:hull}. We formalize this in
Proposition~\ref{prop:dist}.

\begin{proposition}[Regularized width $=2\tau\times$ range-distance]
\label{prop:dist}
Let $\theta_0$ be the minimum-norm solution of $\Sigma_\mathcal{S}\theta=-b$ and
\[
\delta_\mathcal{S}(t)\;:=\;\mathrm{dist}\bigl(c(t),\mathrm{range}(\Sigma_\mathcal{S}^\top)\bigr)
 \;=\;\bigl\|P_{\mathrm{null}(\Sigma_\mathcal{S})}\,c(t)\bigr\|_2 .
\]
Then for every $\tau\ge\|\theta_0\|_2$,
\begin{equation}
\label{eq:prop3}
w_r^\tau(t;\Sigma_\mathcal{S},b)
 \;=\; 2\sqrt{\tau^2-\|\theta_0\|_2^2}\;\,\delta_\mathcal{S}(t)
 \;=\; 2\tau\,\delta_\mathcal{S}(t)\,\bigl(1+o_\tau(1)\bigr),
\qquad \tau\to\infty,
\end{equation}
with the $o_\tau(1)$ term uniform on compact target regions. In particular, for
two candidates $k_1,k_2$ with
$\delta_{\mathcal{S}\cup\{k_1\}}(t)<\delta_{\mathcal{S}\cup\{k_2\}}(t)$
uniformly over $t\in\mathcal{T}$, candidate $k_1$ dominates $k_2$ under the
minimax criterion \eqref{eq:minimax} in the unrestricted limit.
\end{proposition}

\begin{corollary}[Affine-hull distance under a balanced embedding]
\label{cor:hulldist}
Suppose the cross-site design is balanced with a common within-site
$X$-distribution, and the target functional is an isometric (or scalar) linear
embedding of the centered target profile,
$c(t)=L\bigl((t_m,t_r)-\bar c\bigr)$ with $L^\top L=\kappa I$ for some
$\kappa>0$, \emph{and} the moment range is exactly the image under $L$ of the
centered context span,
\[
\mathrm{range}\bigl(\Sigma_\mathcal{S}^\top\bigr)
 \;=\; L\,\mathrm{span}\bigl\{\tilde c^{(s)}:s=1,\dots,S\bigr\}.
\]
(The scaled isometry $L^\top L=\kappa I$ alone does not imply this range
identity; it must be imposed, and it is what the balanced design with common
$X$-distribution delivers.) Then
\[
\delta_\mathcal{S}(t)\;=\;\sqrt{\kappa}\;\,
 \mathrm{dist}\bigl((t_m,t_r),\mathrm{aff}(\mathcal{H}_\mathcal{S})\bigr),
\]
so \eqref{eq:prop3} reduces to a weighted distance from $(t_m,t_r)$ to the
affine hull of the existing contexts.
\end{corollary}

Proposition~\ref{prop:dist} gives the \textbf{affine-span expansion rule}: in
the unrestricted (large-$\tau$) limit, the minimax-optimal candidate is the one
whose addition minimizes $\sup_{t \in \mathcal{T}} \delta_{\mathcal{S}\cup\{k\}}(t)$,
the worst-case distance from the target functional to the moment range. Under
the balanced embedding of Corollary~\ref{cor:hulldist} this is the candidate
whose enlarged \emph{affine hull} leaves no target profile in $\mathcal{T}$ far
from the span of sites. When $\mathcal{T}$ contains points outside
$\mathrm{aff}(\mathcal{H}_\mathcal{S})$ the rule coincides with expanding the
convex hull in the direction of the target region; in general it is an
affine-span, not a convex-hull, criterion.
