\section{Discussion}
\label{sec:extensions}

\paragraph{Effect-ordering (mixed-integer).}
When the restriction set is the effect-ordering polyhedron of Restriction~1 of \citet{boyarsky2026}, the program \eqref{eq:surrogate} becomes a mixed-integer
LP. The locally-constant integer-solution argument of \S1(ii) in \citet{boyarsky2026} extends to this case. On a neighborhood of $\gamma_\mathcal{S}$, the
optimal sign pattern is constant, so the MILP reduces to the LP
\eqref{eq:surrogate} after fixing integer variables. We then perform selection
by \eqref{eq:surrogate} at the fixed pattern. Sign flips across candidate sites
can be detected by re-solving the MILP at the top two or three candidates.

\paragraph{Cost-weighted selection.}
Adding a cost $c_k$ to the objective \eqref{eq:minimax} is straightforward
because the cost term is separable in $k$. The minimax-optimal candidate under
Lagrangian \eqref{eq:lagrangian} is obtained by solving \eqref{eq:surrogate}
with an additional additive penalty. In our setting a cost based on ethical
concerns might penalize candidates that are demographically similar to existing
sites, because such sites do little to broaden the external-validity claim
despite being cheap to reach.

\paragraph{Multiple candidates at once.}
The design problem \eqref{eq:minimax} can be posed over a subset
$\mathcal{J}\subseteq\mathcal{K}$ of candidates to add simultaneously. If the
objective is the \emph{coverage} (rank) gain, $\mathcal{J}\mapsto
\mathrm{rank}(\Sigma_{\mathcal{S}\cup\mathcal{J}})$ is a matroid rank function,
hence submodular, and greedy attains the classical $(1-1/e)$ guarantee
\citep{nemhauser1978analysis}. We conjecture, but do not prove, that the
\emph{width} surrogate inherits approximate submodularity in the rank-monotone
limit; under affine restrictions and unknown $b$ the width is not automatically
submodular, so the greedy guarantee should be read as applying to the pure
coverage objective unless this is established.

\paragraph{Connection to efficient influence functions.}
The minimum-norm multiplier $\lambda^\star$ in \eqref{eq:envelope} coincides with
the Riesz representer in the efficient influence function of
\citet[Eq.~2.9]{boyarsky2026}, so the endpoint \emph{values} $v_u,v_\ell$ at a
fixed candidate and target inherit their debiased-cross-fitting inference.
Inference for the \emph{selected} design is more delicate: the criterion is a
$\min$ over candidates of a $\sup$ over targets of an LP width, which is
non-smooth. A valid confidence statement requires additional regularity --- a
unique worst-case target, a unique minimizing candidate, and active-set
stability --- under which a directional (Danskin/delta) argument applies. We flag
this as a requirement rather than a corollary; absent these conditions the naive
delta method is not justified.

\paragraph{Open questions.}
Four directions are natural follow-ups. First, our analysis holds the moment
identity exact; with an \emph{estimated or relaxed} identity, the tolerance-set
program over $\{\theta:\|\widehat\Sigma\theta+\widehat b\|\le\eta\}$ does widen
as the smallest non-trivial eigenvalue shrinks (Section~\ref{sec:monotone-fail},
(F2)), and a site-selection theory for that relaxed program --- where
conditioning genuinely matters --- is open. Second, the adversarial $b$-prior of
Section~\ref{sec:unknown-b}(3) admits a saddle-point representation but not a
closed-form solution. Existing interior-point solvers handle small instances,
but large candidate pools would benefit from a custom Frank--Wolfe scheme.
Third, in the online-experimentation setting the candidate pool is revealed
sequentially, and the selection must be made without access to the full set.
Adapting \eqref{eq:surrogate} to this regret-minimization formulation is open.
Fourth, the assumption that the within-site $X$-distribution at candidate sites
is known (or has an informative prior) is strong. A distributionally-robust
variant that treats $P_X^{(k)}$ as uncertain over a Wasserstein ball would keep
the theoretical guarantees of the \citet{jeong2020assessing} worst-case program,
at the cost of a more conservative selection.
