\section{Introduction}
\label{sec:intro}

A multi-site experiment supports its external-validity claim through the
\emph{cross-site} variation in site-level context. If the treatment effect is
stable across sites that differ substantially in their moderating attributes,
then it is credible that the effect will transport to a new site whose
moderators lie within the observed range. Conversely, when the observed sites
cover only a small part of the space of site-level moderators, the cross-site
moment identity $\Sigma\theta + b = 0$ is rank-deficient. The target-site
treatment effect at a moderator profile $(t_m,t_r)$ outside the span of observed
sites is then only partially identified, no matter how large the
individual-level samples are \citep*{boyarsky2026}.

An investigator facing this situation has two options. She may \emph{tighten the
identification set} by imposing additional substantive restrictions
$r(\theta)\le 0$ (effect-ordering, sign or monotonicity constraints, norm
bounds, etc.). This trades a sharper bound for additional untestable
assumptions. Or she
may \emph{expand the evidence base} by running a new experiment in an additional
site. The first option is the subject of \citet{boyarsky2026}. In this paper
we address the second.

Specifically, we consider the situation in which the investigator has a small
pool $\mathcal{K} = \{1, \ldots, K\}$ of \emph{candidate} sites. For each
candidate site the investigator knows the site-level context $(C_m^{(k)},
C_r^{(k)})$ in advance, cheaply obtained from administrative data, public
statistics, a pilot survey, or an established literature, but has no
individual-level experimental data. Running the
experiment in any one candidate site carries an investigator-specified cost
$c_k$ (monetary, logistical, ethical). The question is:

\begin{quote}
Given the existing pool of $S$ sites and a range $\mathcal{T}$ of target
profiles to which the investigator wishes to transport the effect, which
candidate site $k^\star \in \mathcal{K}$ most improves external-validity claims,
in the sense of most shrinking the partial-identification width over
$\mathcal{T}$?
\end{quote}

We cast the problem as a \textbf{minimax design}:
\[
k^\star \;\in\; \arg\min_{k\in \mathcal{K}}\; \sup_{(t_m,t_r)\in\mathcal{T}}\;
w_r\!\bigl(t_m,t_r;\; \Sigma_{\mathcal{S}\cup\{k\}}\bigr),
\]
where $w_r(t_m,t_r;\Sigma)$ is the width of the partial-identification interval
under restriction $r$ evaluated at target $(t_m,t_r)$. The key observation is
that the width $w_r$ depends on the candidate site through $\Sigma$, the
\emph{design matrix} of the moment condition, and $\Sigma$ is a function of
known site-level quantities $(C_m, C_r)$ only. This is what makes the design
problem tractable without running the candidate experiments. The right-hand side
$b$ would move once the experiment is run. The site-level context determines the
rank and moment-range geometry, and therefore determines \emph{unrestricted}
finiteness of the width, conditional on feasibility. Under compact restrictions,
however, $b$ also matters: it translates the moment-implied affine slice through
the restriction set and can change the width (Section~\ref{sec:counterexample}).
We therefore treat the context-driven geometry as the design-time object and
evaluate candidates using either an outcome forecast or a robust uncertainty set
for $\Delta b_k$ (Section~\ref{sec:unknown-b}).

\paragraph{Contributions.}
(1) We formalize the site-selection problem in the partial-identification framework of \citet{boyarsky2026}. We show that the partial-identification
width depends on the candidate through a low-rank update of $\Sigma$ (rank at
most two) that is known before the experiment is run. (2) We establish that, in
the unrestricted limit $r \equiv 0$ with mild regularization, the minimax rule
selects the candidate whose addition most reduces the worst-case distance from
the target functional $c(t)$ to the enlarged moment range
(Proposition~\ref{prop:dist}). Under a balanced isometric embedding this becomes
a weighted \emph{affine-span} expansion rule in site-context space
(Corollary~\ref{cor:hulldist}), with the weighting determined by $\mathcal{T}$.
Convex-hull expansion is the right design intuition exactly when the target set
lies outside the existing affine span in target-relevant directions.
(3) Under compact affine restrictions $r(\theta)\le 0$, we derive a tractable
surrogate, a finite LP over the candidate pool, that has the same three-regime
structure as the leave-one-site-out diagnostic of \citet{boyarsky2026}: candidates are \emph{coverage-expanding} (reduce rank-deficiency),
\emph{location-improving} (shift the affine subspace at fixed rank), or
\emph{feasibility-restoring} (make a previously incompatible restriction set
feasible). (4) We show that the minimax design is \emph{not} automatically
monotone in site addition. A rank-preserving candidate whose outcome conflicts
with the existing-pool fit can shift the moment-implied affine subspace to a
less favorable cross-section of the restriction polyhedron, and it can strictly
\emph{increase} the worst-case width. We isolate two screens,
rank expansion (M1) and outcome-consistency (M2), and prove
(Theorem~\ref{thm:monotone}) that the worst-case width is monotone-nonincreasing
under (M2) in the rank-preserving case, and under (M1) whenever the augmented
feasible set remains non-empty --- a condition guaranteed by pairing (M1) with
an outcome-feasibility check, not by (M1) alone. (5) A synthetic
simulation with eight existing sites and six candidates, including a
deliberately conflicting one, confirms both the hull-expansion result and the
non-monotonicity (with $16\%$ of replicates showing strict worsening from the
unscreened candidate, and none from any screened candidate). (6) We sketch
extensions to the
mixed-integer effect-ordering formulation and to cost-weighted objectives, and
defer complete proofs to Appendix~\ref{sec:appendix}.

\paragraph{Positioning.}
The site-selection question is the \emph{forward} version of the
leave-one-site-out diagnostic in Section~4.4 of \citet{boyarsky2026}, which asks which existing donor sites are essential to a reported bound. Our problem
has the same three-regime taxonomy as that diagnostic, but we apply it to a
\emph{counterfactual} addition rather than a realized removal. It also
complements classical optimal experimental design (D-, G-, and I-optimality),
which operates within a single population under point identification \citep{atkinson2007optimum, pukelsheim2006optimal}. In our setting the design object is
not an individual-level allocation of treatment but a site-level choice of
context, and the loss is the width of a partial-identification interval
rather than the variance of a point estimator. The minimax objective is natural
here because site selection is a discrete, one-time decision that should do well
across the different target profiles the investigator cares about.
