\section{Monotonicity: When Adding a Site Can Hurt}
\label{sec:monotonicity}

One might expect that the minimax design problem \eqref{eq:minimax} is
bounded above by the existing-pool width. That is, one might expect that
$\sup_t w_r(t;\Sigma_{\mathcal{S}\cup\{k\}})\le \sup_t
w_r(t;\Sigma_\mathcal{S})$ for every candidate $k$, so that the design problem
is only a question of how much we gain. This is false. Adding a site can
strictly \emph{increase} the worst-case width, and in some cases it can make the
program infeasible. This section traces the failure modes and isolates the
conditions
under which monotone improvement is guaranteed.

\subsection{Why monotone improvement can fail}
\label{sec:monotone-fail}

Recall from Section~\ref{sec:augmentation} that two things change when a candidate
site is added: the moment matrix $\Sigma$ acquires a rank-$\le 2$ update
$\Delta\Sigma_k$ in the row directions spanned by the residualized context
$(u_m^{(k)},u_r^{(k)})$, and the right-hand side $b$ shifts by an
outcome-dependent amount $\Delta b_k$. The first update is monotone in PSD order:
$\Sigma_{\mathcal{S}\cup\{k\}} \succeq \Sigma_\mathcal{S}$, so
$\mathrm{null}(\Sigma_{\mathcal{S}\cup\{k\}})\subseteq
 \mathrm{null}(\Sigma_\mathcal{S})$. The second is not monotone in any sense.
Two mechanisms can widen the exact program \eqref{eq:bounds}; a third,
conditioning, cannot, and is recorded only to forestall it:

\paragraph{(F1) Rank-preserving shift.}
If $(u_m^{(k)},u_r^{(k)})\in \mathrm{range}(\Sigma_\mathcal{S})$, the rank of
$\Sigma$ does not change, and the new feasible set is parallel to the old
in the sense $\theta'+\mathrm{null}(\Sigma_\mathcal{S})$ for some
$\theta'\ne\theta_\mathcal{S}^\star$ whenever
$y_k\ne (u_m^{(k)},u_r^{(k)})^\top \theta_\mathcal{S}^\star$. This parallel
slice intersects the restriction polyhedron $\mathcal{R}$ at a different
polytope, whose projection onto the target functional can be longer than the
original. For example, this happens when $\mathcal{R}$ is asymmetric around
$\theta_\mathcal{S}^\star$ and the shift moves the slice into a wider
cross-section of $\mathcal{R}$.

\paragraph{(F2) Conditioning does \emph{not} widen the exact LP.}
One might expect a mechanism from conditioning: in the formulation of
\citet{boyarsky2026}, $\Sigma$ is a sample average over the pooled
$(\sum_s n_s+n_k)$ observations, so adding a candidate re-weights the
existing-pool contribution by $n/(n+n_k)$ and can shrink the smallest
non-trivial eigenvalue $\sigma_{\min,+}(\Sigma_{\mathcal{S}\cup\{k\}})$. This
does not enlarge the exact feasible set. With equality constraints
$\Sigma\theta=-b$, the set $\mathcal{L}(\Sigma,b)\cap\mathcal{R}$ is determined
by the row space, the null space, and a particular solution; it is invariant to
eigenvalue magnitudes, and any re-weighting that preserves the row space
leaves $\mathcal{L}(\Sigma,b)$ unchanged. Conditioning bites only once the moment
identity is \emph{estimated or relaxed} to a tolerance set
$\{\theta:\|\widehat\Sigma\theta+\widehat b\|\le\eta\}$, whose width does grow as
$\sigma_{\min,+}$ shrinks. We do not analyze that tolerance-set program in this
paper; Section~\ref{sec:unknown-b} treats the related but distinct problem of
uncertainty in $\Delta b_k$ under the exact moment identity, and we flag the
relaxed-moment analysis as an open question in
Section~\ref{sec:extensions}. For the exact LP, only the rank-preserving shift
(F1) and the restriction-set conflict (F3) can do harm.

\paragraph{(F3) Restriction-set conflict.}
If the candidate's outcome update $\Delta b_k$ shifts the moment-implied affine
subspace
$\{\Sigma_{\mathcal{S}\cup\{k\}}\theta = -b_{\mathcal{S}\cup\{k\}}\}$ outside the
restriction polyhedron $\mathcal{R}$, the LP becomes infeasible and the
partial-identification interval is empty. This is the feasibility-breaking case
of regime (C) in Section~\ref{sec:regimes}.

The simulation in Section~\ref{sec:simulation} demonstrates (F1) directly: an
outcome shock of magnitude $\Delta = 20$ at a rank-preserving candidate $k_5$
produces a strict increase in the worst-case width in $8/50$ Monte-Carlo
replicates, with no rank or feasibility change.

\subsection{An explicit counterexample}
\label{sec:counterexample}

We give a fully worked $d_g=2$ example, both because the geometry is easy to see
and because the same construction extends to the multivariate simulations of
Section~\ref{sec:simulation}.

\paragraph{Setup.}
Take $d_g=2$, $S=1$ existing site with context $c^{(1)}=(1,1)^\top$ and outcome
$y_1=2$. The simplified moment is
$\Sigma_\mathcal{S}=c^{(1)}{c^{(1)}}^\top=\bigl(\begin{smallmatrix}1&1\\1&1\end{smallmatrix}\bigr)$
with $\mathrm{rank}=1$, and $b_\mathcal{S}=-c^{(1)}y_1=(-2,-2)^\top$. The
moment-implied subspace is $\{(\theta_1,\theta_2):\theta_1+\theta_2=2\}$, a line
in $\mathbb{R}^2$. Take the (asymmetric) box restriction
$\mathcal{R}=[0,2]\times[-1,1]$ and the target functional $c(t)=(1,0)^\top$. The
feasible segment is $\{(\theta_1,2-\theta_1):\theta_1\in[1,2]\}$, with
$w_r\bigl(t;\Sigma_\mathcal{S},b_\mathcal{S}\bigr)=1$.

\paragraph{Candidate.}
Add a rank-preserving candidate $k_5$ with $c^{(k_5)}=c^{(1)}=(1,1)^\top$ and
conflicting outcome $y_{k_5}=0\ne 2= c^{(k_5)\top}\theta_\mathcal{S}^\star$,
where $\theta_\mathcal{S}^\star=(1,1)^\top$ is the minimum-norm solution. Then
$\Sigma_{\mathcal{S}\cup\{k_5\}}=2\,c^{(1)}{c^{(1)}}^\top$ (still rank 1), and
$b_{\mathcal{S}\cup\{k_5\}}=b_\mathcal{S}-c^{(k_5)}y_{k_5}=(-2,-2)^\top$, giving
moment-implied line $\theta_1+\theta_2=1$. The new feasible segment is
$\{(\theta_1,1-\theta_1):\theta_1\in[0,2]\}$, with
\[
w_r\bigl(t;\Sigma_{\mathcal{S}\cup\{k_5\}},
 b_{\mathcal{S}\cup\{k_5\}}\bigr) \;=\; 2 \;>\; 1
 \;=\; w_r\bigl(t;\Sigma_\mathcal{S},b_\mathcal{S}\bigr).
\]
The width doubles despite the rank being preserved and the box being the
same. Panel (A) of Figure~\ref{fig:fig2} displays the two parallel slices inside
the box.

The construction generalizes. In dimension $d_g\ge 2$, any rank-preserving
candidate with outcome $y_k\ne c^{(k)\top}\theta_\mathcal{S}^\star$ produces a
parallel shift of the moment-implied subspace. Whenever $\mathcal{R}$ is
asymmetric around $\theta_\mathcal{S}^\star$, the shifted slice can cut
$\mathcal{R}$ at a polytope of larger $t$-extent.

\subsection{Sufficient conditions for monotone improvement}
\label{sec:sufficient}

We now isolate two assumptions under which the worst-case width is
monotone-nonincreasing in site addition. The two assumptions are independent,
but neither is unconditionally sufficient on its own: (M2) is sufficient in the
rank-preserving case, while (M1) requires in addition that the augmented
feasible set remain non-empty (Theorem~\ref{thm:monotone}). Each has a
design-time (pre-experiment) counterpart that can be used to screen the
candidate pool.

\paragraph{Assumption (M1) --- Rank-Expansion Screen.}
The candidate's residualized context lies outside the row space of the
existing pool:
\begin{equation}
\label{eq:m1}
(u_m^{(k)},u_r^{(k)})\;\notin\;\mathrm{range}\bigl(\Sigma_\mathcal{S}\bigr).
\end{equation}

\paragraph{Assumption (M2) --- Outcome-Consistency Screen.}
The candidate's outcome forecast is consistent with the existing pool's
minimum-norm fit:
\begin{equation}
\label{eq:m2}
y_k \;=\; (u_m^{(k)},u_r^{(k)})^\top \theta_\mathcal{S}^\star,
\end{equation}
where $\theta_\mathcal{S}^\star$ is the minimum-norm solution to
$\Sigma_\mathcal{S}\theta = -b_\mathcal{S}$.

The two screens differ in what can be checked before the candidate experiment is
run. (M1) is fully checkable at design time: it is a rank test on
$(u_m^{(k)},u_r^{(k)})$ against the existing-pool SVD. (M2), as stated, is a
condition on the \emph{realized} candidate outcome moment $y_k$, which is not
observable at design time. Its design-time counterpart is the \emph{forecast
screen} $y_k^{\rm prior}\approx u^\top\theta_\mathcal{S}^\star$, where
$y_k^{\rm prior}$ is a model- or prior-based forecast (e.g.\ the existing-pool
OLS prediction at the candidate context). The deterministic conclusions of
Theorem~\ref{thm:monotone} apply to the realized $y_k$; the forecast screen is a
sufficient condition only for the forecasted moment, or a high-probability
screen when the prior concentrates near $u^\top\theta_\mathcal{S}^\star$. The
two assumptions imply different consequences. (M1) strictly reduces the null
space. In the unrestricted large-$\tau$ limit this strictly reduces the width
for targets loading the resolved direction (Proposition~\ref{prop:dist}). Under
compact restrictions, strict width reduction requires the added constraint to
cut off a maximizing or minimizing face of $\mathcal{F}_\mathcal{S}$, and
monotone nonincrease requires
$\mathcal{F}_\mathcal{S}\cap\{\theta:u^\top\theta=y_k\}\ne\varnothing$. (M2)
leaves the moment-implied affine subspace unchanged in the rank-preserving case
and prevents the feasibility-breaking shifts of
Section~\ref{sec:monotone-fail}.

\begin{theorem}[Monotone improvement under (M1) or (M2)]
\label{thm:monotone}
Assume the additive PSD update $\Sigma_{\mathcal{S}\cup\{k\}}=\Sigma_\mathcal{S}+uu^\top$,
$b_{\mathcal{S}\cup\{k\}}=b_\mathcal{S}-uy_k$, the consistency condition
$b_\mathcal{S}\in\mathrm{range}(\Sigma_\mathcal{S})$, and
$\mathcal{F}_\mathcal{S}\ne\varnothing$.
\begin{enumerate}
\item[(i)] (Rank-preserving, (M2).) If $u\in\mathrm{range}(\Sigma_\mathcal{S})$
  and $y_k=u^\top\theta_\mathcal{S}^\star$, then
  $\mathcal{F}_{\mathcal{S}\cup\{k\}}=\mathcal{F}_\mathcal{S}$, and the width is
  unchanged at every target.
\item[(ii)] (Rank-expanding, (M1).) If $u\notin\mathrm{range}(\Sigma_\mathcal{S})$,
  then
  $\mathcal{F}_{\mathcal{S}\cup\{k\}}=\mathcal{F}_\mathcal{S}\cap\{\theta:u^\top\theta=y_k\}$.
  If this set is non-empty --- in particular under (M2),
  $y_k=u^\top\theta_\mathcal{S}^\star$, whenever $\theta_\mathcal{S}^\star\in\mathcal{R}$
  --- then $\mathcal{F}_{\mathcal{S}\cup\{k\}}\subseteq\mathcal{F}_\mathcal{S}$ and
  for every target $t$,
  $w_r(t;\Sigma_{\mathcal{S}\cup\{k\}},b_{\mathcal{S}\cup\{k\}})\le
   w_r(t;\Sigma_\mathcal{S},b_\mathcal{S})$. If instead the set is empty, the
  augmented partial-ID interval is empty (failure mode (F3)) and the comparison
  is vacuous.
\end{enumerate}
Hence the worst-case width is monotone non-increasing whenever the augmented
feasible set is non-empty. In case (ii) the inequality is strict at a target $t$
only if the new constraint $u^\top\theta=y_k$ cuts off the maximizing or
minimizing face of $\mathcal{F}_\mathcal{S}$ in direction $c(t)$; a non-zero
component of $c(t)$ along $u_\perp$ is necessary but not sufficient once
$\mathcal{R}$ already binds.
\end{theorem}

Theorem~\ref{thm:monotone} is proved in Appendix~\ref{sec:proof-thm1}. The key
step is the algebraic identity \eqref{eq:identity}, which shows that
$\Sigma_{\mathcal{S}\cup\{k\}}\theta+b_{\mathcal{S}\cup\{k\}}=
\Sigma_\mathcal{S}\theta+b_\mathcal{S}+u\cdot(u^\top\theta-y_k)$, together with
the consistency hypothesis $b_\mathcal{S}\in\mathrm{range}(\Sigma_\mathcal{S})$.

\paragraph{Remark (Practical use).}
The pair (M1, M2) is not exhaustive, because a candidate failing both can
still improve the width. But it does provide a finite, computable screen. In
practice we recommend the following. First, run the SVD-based test \eqref{eq:m1}
on every candidate, and mark those that pass and whose forecasted outcome
keeps $\mathcal{F}_\mathcal{S}\cap\{\theta:u^\top\theta=y_k\}\ne\varnothing$
(an LP feasibility check) as safe rank-expanders; passing (M1) alone is
not a no-harm guarantee. Second, among the rank-preserving candidates, check
\eqref{eq:m2} against the existing-pool OLS prediction, and mark those that pass
as safe consistent candidates. Third, report the minimax
\eqref{eq:minimax} only over
the safe subset of the candidate pool, or report the unsafe candidates
separately as ``diagnostic-only'' sites whose addition could be informative but
whose worst-case width is not guaranteed to improve.

\paragraph{Remark (Cost-aware extension).}
When candidates carry a cost $c_k$, we combine the safe-subset screening of
(i)--(iii) above with the Lagrangian \eqref{eq:lagrangian}, and the optimal
candidate is the cheapest member of the safe subset that achieves the minimax
target. Unsafe candidates can be admitted only with an explicit risk premium
$\rho_k\ge 0$ added to their cost, set from the upper bound on
$w_r(\cdot;\Sigma_{\mathcal{S}\cup\{k\}})- w_r(\cdot;\Sigma_\mathcal{S})$ in the
perturbation bound \eqref{eq:envelope}.

\subsection{Discussion: why the affine-span rule is only sufficient}
\label{sec:hull-only-sufficient}

Proposition~\ref{prop:dist} of Section~\ref{sec:hull-distance} shows that, in
the large-$\tau$ unrestricted limit, the optimal candidate is the one whose
addition minimizes $\sup_{t\in\mathcal{T}}\delta_{\mathcal{S}\cup\{k\}}(t)$.
Theorem~\ref{thm:monotone} refines this. The affine-span (hull-expansion) rule
is sufficient for monotone improvement when feasibility is
preserved: an outside-hull candidate satisfies (M1), and if its outcome keeps
$\mathcal{F}_{\mathcal{S}\cup\{k\}}\ne\varnothing$ the width cannot increase. It
is not necessary: an interior candidate satisfying (M2) also guarantees no
worsening. Conversely, a hull-expander with an adversarial outcome can empty or
badly shift the feasible set (failure mode (F3)); (M1) is necessary in the rank
sense but not sufficient against shifts.

The cleanest characterization combines both:

\begin{quote}
A candidate $k$ is width-monotone safe if either (i) its residualized
context is outside $\mathrm{range}(\Sigma_\mathcal{S})$ and the outcome
shift $\Delta b_k$ is small enough that the hyperplane $u^\top\theta=y_k$
intersects the existing feasible set,
\[
\mathcal{F}_\mathcal{S}\cap\{\theta:u^\top\theta=y_k\}\ne\varnothing,
\qquad\text{i.e.}\qquad
\exists\,\theta\in\mathcal{R}\ \text{with}\
\Sigma_\mathcal{S}\theta=-b_\mathcal{S},\ u^\top\theta=y_k,
\]
or (ii) its context is inside the
existing range and its outcome matches the existing OLS prediction (modulo
tolerance). Intersecting $\mathcal{R}$ alone is not enough: a hyperplane can cut
$\mathcal{R}$ yet miss the moment slice
$\mathcal{L}(\Sigma_\mathcal{S},b_\mathcal{S})\cap\mathcal{R}$ entirely.
\end{quote}

This is the operational characterization we use in Section~\ref{sec:simulation}.

\subsection{Adverse no-shrink risk after context-based site selection}
\label{sec:adverse-no-shrink-ri}

The minimax rule is a design-time rule: it uses the candidate site's context to
identify sites whose addition should shrink the external-validity bound. This
calculation is possible before the candidate experiment is run because the
candidate's contribution to the moment matrix, $\Delta\Sigma_k$, is determined by
pre-randomization context and covariate information. The right-hand side,
however, shifts by an outcome-dependent amount $\Delta b_k$, which is not known
until the selected experiment is actually run. Thus a site may look promising
from its context, but the realized outcome update may fail to deliver the
predicted shrinkage.

We formalize this failure as an adverse no-shrink, or more generally
under-delivery, event. Let
\[
\widehat W_S
:=
\sup_{t\in T}
w_r(t;\widehat\Sigma_S,\widehat b_S)
\]
be the existing-pool worst-case width. For candidate $k$, let
$\widehat\delta_k^{\mathrm{ctx}}$ be any pre-specified, pre-randomization
forecast for the candidate's right-hand-side update. For example,
$\widehat\delta_k^{\mathrm{ctx}}$ may be induced by the existing-pool prediction
$y_k=u_k^\top\widehat\theta_S^\star$, by the center of the prior set
$B$ from Section 5.3, or by a meta-analytic forecast. Define the
context-predicted post-addition width
\[
\widehat W_k^{\mathrm{ctx}}
:=
\sup_{t\in T}
w_r\!\left(
t;
\widehat\Sigma_{S\cup\{k\}},
\widehat b_S+\widehat\delta_k^{\mathrm{ctx}}
\right),
\]
and the context-predicted gain
\[
\widehat G_k^{\mathrm{ctx}}
:=
\widehat W_S-\widehat W_k^{\mathrm{ctx}}.
\]
The case of interest is $\widehat G_k^{\mathrm{ctx}}>0$: based on context, the
candidate is predicted to shrink the worst-case partial-identification width.

After the selected candidate experiment is run, the realized treatment assignment
determines the observed candidate-site outcome contribution and hence the realized
update to $b$. To obtain an exact finite-sample benchmark for adverse
realizations, we use the randomization design within the selected site.

Let $\mathcal F_0$ denote all information available before the treatment
assignment in the selected candidate site:
\[
\mathcal F_0
=
\sigma\!\left(
D_S,\,
\{Z_k,\Omega_k,Q_k,G_k\}_{k\in K},\,
T,\,
R,\,
U
\right),
\]
where $D_S$ is the existing-site data, $Z_k$ contains candidate $k$'s
pre-randomization information, $\Omega_k$ is its assignment space, $Q_k$ is its
known randomization distribution, $G_k$ is a finite randomization group acting on
$\Omega_k$, and $U$ is optional tie-breaking randomness. The selected site is
\[
K^\star=\kappa(\mathcal F_0),
\]
so site selection may depend on the minimax rule, candidate contexts, costs, the
target region, restrictions, and tie-breaking randomness, but not on the selected
site's treatment assignment or post-treatment outcomes.

For the selected site $K^\star=k$, let $A_k\in\Omega_k$ be the realized
assignment. We assume the assignment distribution is invariant under the
randomization group:
\[
Q_k(ga)=Q_k(a)
\qquad
\text{for every }g\in G_k,\ a\in\Omega_k.
\tag{RI}
\]
Complete randomization is the special case in which $G_k$ is the symmetric group
on units and $\Omega_k$ fixes the number treated. Block randomization is the
case in which $G_k$ is the product of the within-block symmetric groups.

Let $H_0(\eta)$ be a sharp benchmark for the candidate-site potential outcomes.
Sharpness means that, given the observed data and $\eta$, the missing potential
outcomes can be imputed under every assignment $a\in\Omega_k$. Let
$D_k^\eta(a)$ denote the candidate-site data that would be observed under
assignment $a$ after this imputation, and let
\[
\widehat{\Delta b}_k(a;\eta)
\]
be the corresponding candidate-site update to the right-hand side. Define the
post-addition worst-case width under assignment $a$ as
\[
\widehat W_k(a;\eta)
:=
\sup_{t\in T}
w_r\!\left(
t;
\widehat\Sigma_{S\cup\{k\}},
\widehat b_S+\widehat{\Delta b}_k(a;\eta)
\right).
\]
The realized gain under assignment $a$ is
\[
\widehat G_k(a;\eta)
:=
\widehat W_S-\widehat W_k(a;\eta).
\]

For $q\in[0,1]$, define the adverse $q$-under-delivery event
\[
\mathcal A_{k,q}(a;\eta)
:=
\left\{
\widehat G_k(a;\eta)
\le
q\,\widehat G_k^{\mathrm{ctx}}
\right\}.
\tag{6.5}
\]
Equivalently,
\[
\mathcal A_{k,q}(a;\eta)
=
\left\{
\widehat W_k(a;\eta)
\ge
\widehat W_S-q\,\widehat G_k^{\mathrm{ctx}}
\right\}.
\]
Thus $q=0$ corresponds to no shrinkage or worsening:
\[
\mathcal A_{k,0}(a;\eta)
=
\left\{
\widehat W_k(a;\eta)\ge \widehat W_S
\right\}.
\]
For $q=1/2$, the event says that the realized experiment delivered at most half
of the context-predicted gain. For $q=1$, it says that the realized experiment
underperformed the context-only forecast.

For an assignment $a$, write
\[
\mathcal O_k(a)
:=
\{ga:g\in G_k\}
\]
for its orbit under the randomization group. The randomization-inference estimate
of adverse under-delivery risk is
\[
\widehat\pi_{k,q}^{\mathrm{RI}}(\eta)
:=
\frac{1}{|\mathcal O_k(A_k^{\mathrm{obs}})|}
\sum_{a\in\mathcal O_k(A_k^{\mathrm{obs}})}
\mathbf 1\{\mathcal A_{k,q}(a;\eta)\}.
\tag{6.6}
\]
This is the fraction of assignments, among those allowed by the actual
randomization design, under which the candidate would fail to deliver at least a
$q$-fraction of the context-predicted shrinkage.

\begin{theorem}[Post-selection randomization inference for adverse no-shrink risk]
\label{thm:adverse-no-shrink-ri}
Assume:

\begin{enumerate}
\item The selected site satisfies $K^\star=\kappa(\mathcal F_0)$, so selection
uses only pre-randomization information.

\item Conditional on $\mathcal F_0$ and $K^\star=k$, the selected-site assignment
$A_k$ is drawn from the known design $Q_k$ on $\Omega_k$.

\item The randomization design is invariant under the finite group $G_k$, i.e.
\[
Q_k(ga)=Q_k(a)
\qquad
\forall g\in G_k,\ a\in\Omega_k.
\]

\item The benchmark $H_0(\eta_0)$ is true and sharp, so
$\widehat W_k(a;\eta_0)$ is computable for every $a\in\Omega_k$.

\item The context-predicted gain $\widehat G_k^{\mathrm{ctx}}$ is
$\mathcal F_0$-measurable.
\end{enumerate}

Then, for every $q\in[0,1]$,
\[
\Pr_{\eta_0}
\left(
\mathcal A_{k,q}(A_k;\eta_0)
\mid
\mathcal F_0,\,
K^\star=k,\,
\mathcal O_k(A_k^{\mathrm{obs}})
\right)
=
\widehat\pi_{k,q}^{\mathrm{RI}}(\eta_0).
\tag{6.7}
\]
In particular, for $q=0$,
\[
\Pr_{\eta_0}
\left(
\widehat W_k(A_k;\eta_0)\ge \widehat W_S
\mid
\mathcal F_0,\,
K^\star=k,\,
\mathcal O_k(A_k^{\mathrm{obs}})
\right)
=
\widehat\pi_{k,0}^{\mathrm{RI}}(\eta_0).
\tag{6.8}
\]
Thus $\widehat\pi_{k,0}^{\mathrm{RI}}(\eta_0)$ is the exact conditional
randomization probability that the selected site fails to shrink the
worst-case bound, even though its context predicted shrinkage.

Moreover, define the adverse-severity statistic
\[
T_{k,q}^{\mathrm{adv}}(a;\eta)
:=
\left[
\widehat W_k(a;\eta)
-
\left\{
\widehat W_S-q\,\widehat G_k^{\mathrm{ctx}}
\right\}
\right]_+,
\tag{6.9}
\]
and the randomization $p$-value
\[
p_{k,q}^{\mathrm{adv}}(\eta)
:=
\frac{1}{|\mathcal O_k(A_k^{\mathrm{obs}})|}
\sum_{a\in\mathcal O_k(A_k^{\mathrm{obs}})}
\mathbf 1
\left\{
T_{k,q}^{\mathrm{adv}}(a;\eta)
\ge
T_{k,q}^{\mathrm{adv}}(A_k^{\mathrm{obs}};\eta)
\right\}.
\tag{6.10}
\]
Under $H_0(\eta_0)$, for every $\alpha\in[0,1]$,
\[
\Pr_{\eta_0}
\left(
p_{k,q}^{\mathrm{adv}}(\eta_0)\le \alpha
\mid
\mathcal F_0,\,
K^\star=k,\,
\mathcal O_k(A_k^{\mathrm{obs}})
\right)
\le
\alpha.
\tag{6.11}
\]
Consequently,
\[
\Pr_{\eta_0}
\left(
p_{k,q}^{\mathrm{adv}}(\eta_0)\le \alpha
\mid
\mathcal F_0,\,
K^\star=k
\right)
\le
\alpha,
\qquad
\Pr_{\eta_0}
\left(
p_{k,q}^{\mathrm{adv}}(\eta_0)\le \alpha
\right)
\le
\alpha.
\tag{6.12}
\]
\end{theorem}

\begin{remark}[Interpretation]
The quantity $\widehat\pi_{k,0}^{\mathrm{RI}}$ answers the question:
among the assignments that could have occurred in the selected site under the
actual randomization design, what fraction would have produced no shrinkage or
worsening of the worst-case external-validity bound? The statistic
$p_{k,0}^{\mathrm{adv}}$ answers a related severity question: conditional on the
context-consistent benchmark, how unusual was the adverse realization we
observed?

This is a post-experiment, design-based quantity. It is exact because it relies
only on the known treatment-randomization mechanism inside the selected site.
It is not a claim that candidate sites themselves were randomly sampled, nor is
it a model-free pre-experiment probability over unknown potential outcomes.
Before running the candidate experiment, an analogous design-stage risk must be
model-based, for example
\[
\pi_{k,q}^{\mathrm{pred}}
:=
\Pr_{\Delta b_k\sim\Pi_k}
\left(
\sup_{t\in T}
w_r(t;\widehat\Sigma_{S\cup\{k\}},\widehat b_S+\Delta b_k)
\ge
\widehat W_S-q\,\widehat G_k^{\mathrm{ctx}}
\ \middle|\ \mathcal F_0
\right),
\]
where $\Pi_k$ is a pre-specified predictive distribution for the candidate's
outcome-dependent update. The randomization-inference quantity
$\widehat\pi_{k,q}^{\mathrm{RI}}$ is the exact post-experiment analogue obtained
after the selected experiment has actually been run.
\end{remark}

\begin{remark}[Recommended reporting]
For the selected site $K^\star$, report three numbers:
\[
\widehat G_{K^\star}^{\mathrm{ctx}},
\qquad
\widehat G_{K^\star}^{\mathrm{obs}}
=
\widehat W_S-\widehat W_{K^\star}(A_{K^\star}^{\mathrm{obs}};\eta),
\qquad
\widehat\pi_{K^\star,0}^{\mathrm{RI}}.
\]
The first is the shrinkage promised by context. The second is the shrinkage
actually delivered by the realized experiment. The third is the exact
randomization probability of no shrinkage or worsening under the selected
site's assignment mechanism. A context-promising site with small
$\widehat\pi_{K^\star,0}^{\mathrm{RI}}$ is robust to randomization-induced
outcome updates; a site with large $\widehat\pi_{K^\star,0}^{\mathrm{RI}}$ is
fragile, even if its context looked favorable ex ante.
\end{remark}