\section{The Site-Selection Problem}
\label{sec:problem}

\subsection{Setup}
\label{sec:problem-setup}

We observe outcomes from $S$ existing sites, pooled as
$\mathcal{D}_\mathcal{S} = \{(Y_i, A_i, X_i, C_{m,i}, C_{r,i})\}_{i=1}^n$. A
\textbf{candidate pool} $\mathcal{K} = \{1, \ldots, K\}$ consists of $K$
prospective sites for which the site-level context $(C_m^{(k)}, C_r^{(k)})$ is
observed but no individual-level data has been collected. For each candidate we
assume the investigator knows (or can assume a prior on) the within-site
distribution of the individual-level covariates $X$. This is the ``some prior on
$X$'' in our motivating question, and it is necessary because $\Sigma$ depends
on $\mathbb{E}_X[\mathrm{Cov}(C_\bullet, C_\bullet \mid X)]$. In the simplest
case, the investigator assumes $X$ at candidate site $k$ is drawn from the same
distribution as at an existing reference site. In the most refined case, the
investigator uses a demographic prior fitted to data. This additional input is
similar to the pre-registered prior used in two-stage adaptive designs. It is an
assumption, not a free parameter.

The investigator also specifies:
\begin{itemize}
\item a \textbf{target region} $\mathcal{T} \subseteq \mathbb{R}^{d_M+d_I}$ of
  context profiles over which she cares about transportability (a discrete set of
  ``benchmark'' profiles, or a continuous region such as a box around the
  marginal mean of the target population);
\item a \textbf{restriction set} $\mathcal{R} = \{\theta : r(\theta) \le 0\}$
  assumed compact;
\item optionally, a \textbf{cost} $c_k \ge 0$ per candidate site.
\end{itemize}

\subsection{The site-augmentation update}
\label{sec:augmentation}

When a candidate site $k$ is added, the moment matrix updates from
$\Sigma_{\mathcal{S}}$ to
$\Sigma_{\mathcal{S}\cup\{k\}}
 = \Sigma_{\mathcal{S}} + \Delta\Sigma_k(C_m^{(k)}, C_r^{(k)}; P_X^{(k)})$,
where $\Delta\Sigma_k$ depends on the candidate's site-level context and on the
investigator's assumed within-site $X$-distribution but \emph{not} on its
outcomes. The only structural facts we use are that this update is \emph{positive
semidefinite} and of \emph{rank at most two}: there is a $d_g\times 2$ factor
$U_k$ whose columns are the residualized candidate-context directions, and a
$2\times 2$ matrix $A_k\succeq 0$, such that
\begin{equation}
\label{eq:dsigma}
\Delta\Sigma_k \;=\; U_k\,A_k\,U_k^\top,
\qquad A_k\succeq 0,
\qquad \operatorname{rank}\bigl(U_k A_k U_k^\top\bigr)\le 2,
\end{equation}
where $(u_m, u_r) := \bigl(C_m^{(k)}, C_r^{(k)}\bigr) - \bar C_X^{(k)}$ with
$\bar C_X^{(k)} = \mathbb{E}_{P_X^{(k)}}[(C_m, C_r) \mid X]$ are the residuals of
the site-level context after projecting out the individual-level covariate
dependence at the candidate site, and the columns of $U_k$ are built from
$(u_m,u_r)$. Positive semidefiniteness gives
$\Sigma_{\mathcal{S}\cup\{k\}}\succeq\Sigma_\mathcal{S}$, hence
$\mathrm{null}(\Sigma_{\mathcal{S}\cup\{k\}})\subseteq\mathrm{null}(\Sigma_\mathcal{S})$
--- the monotone-in-rank property we use throughout
Sections~\ref{sec:hull}--\ref{sec:monotonicity}. The explicit block form of
$U_k$ and $A_k$ implied by Equation~(A.9) of \citet{boyarsky2026}, together with
its PSD verification, is recorded in Appendix~\ref{sec:proof-block}; the planned
candidate sample size $n_k$ enters only through the positive scale of $A_k$.

The right-hand side $b$ also updates, from $b_\mathcal{S}$ to
$b_{\mathcal{S}\cup\{k\}}$, but the new right-hand side depends on the candidate
site's \emph{outcomes} and is therefore unknown until the experiment is run. We
return to this in Section~\ref{sec:unknown-b}. For most of our analysis the
width depends on $b$ only through a compact-translation argument that does not
affect the first-order ranking of candidates.

\subsection{The minimax design problem}
\label{sec:minimax-problem}

With the site-augmentation update in hand, we define the selection problem
\begin{equation}
\label{eq:minimax}
k^\star \;\in\; \arg\min_{k\in\mathcal{K}}\;
 \sup_{(t_m,t_r)\in\mathcal{T}}\;
 w_r\!\bigl(t_m,t_r;\, \Sigma_{\mathcal{S}\cup\{k\}},\, b_{\mathcal{S}\cup\{k\}}\bigr).
\end{equation}
When costs $c_k$ are specified, the natural Lagrangian form is
\begin{equation}
\label{eq:lagrangian}
k^\star_\kappa \;\in\; \arg\min_{k\in\mathcal{K}}\;
 \sup_{(t_m,t_r)\in\mathcal{T}}\;
 w_r\!\bigl(t_m,t_r;\, \Sigma_{\mathcal{S}\cup\{k\}}\bigr)
 \;+\; \kappa\, c_k,
\end{equation}
with Lagrange multiplier $\kappa \ge 0$ reflecting the marginal willingness to
pay for a unit reduction in worst-case width. All results below extend directly
to \eqref{eq:lagrangian} because the cost term is separable in $k$.

Because $b$ is not known before the candidate experiment is run, we evaluate the
width in \eqref{eq:minimax} at a \emph{robustified} $b$ that maximizes the width
over a compact uncertainty set $\mathcal{B}$ consistent with the investigator's
prior beliefs about candidate-site outcomes. In the simplest case, which we
focus on from here, $\mathcal{B}$ is a symmetric norm ball around the
existing-pool $b$. This includes the ``no-information'' prior and is what we use
in our simulations.
